% filepath: cover_letter.tex
\documentclass[10pt]{letter}
\usepackage{hyperref}

% \address{
%     Jose A. Cortes \\
%     Department of Mathematics \\
%     University of Texas at Arlington \\
%     % Arlington, TX 76019, USA \\
%     % \href{mailto:jose.cortes@uta.edu}{jose.cortes@uta.edu}
% }

\signature{
    % Jose A. Cortes \\
    Primary Author \\
    On behalf of all authors
}

\begin{document}

\begin{letter}{
    % The Editor-in-Chief \\
    % Nuclear Instruments and Methods in Physics Research - Section B (NIM-B)
}

\opening{Dear Editor,}

The submission "Simulation and Combined Spectral Analysis for In-Situ Soil Elemental Content Measurement" is a continuation of work previously published in *Nuclear Instruments and Methods in Physics Research - Section B*.

This paper expands simulations for and improves the accuracy of the in-situ soil elemental content measurement, a critical task for agricultural monitoring. Our work focuses on the analysis of gamma-ray spectra generated from neutron-stimulated soil samples, a technique used for rapid, non-destructive, mobile analysis.

The study simulates gamma spectra from various soil compositions. We investigate, compare and combine two conventional analysis techniques: peak fitting and endmember fitting. Our results demonstrate a significant performance increase, showing the best method is an ensemble method that combines both into a single multivariate calibration model solved via Singular Value Decomposition.

We believe this work is a good fit for NIM-B's scope. This application, using the behaviour of simulated materials of relevance to environmental science subjected to ionising radiation show-cases analytical capabilities of in-situ measurement techniques using gamma ray detectors. 

We confirm that this manuscript is original, has not been published previously, and is not under consideration for publication elsewhere. All authors have approved the manuscript and agree with its submission to NIM-B.

Thank you for your time and consideration. We look forward to hearing from you.

\closing{Best regards,}
 
\end{letter}

\end{document}